Consider a\deleted{n acyclic} multi-threaded \cc
program \added{$P$ $:=$ $\parallel_{i\in \text{\tt TID}} P_i$, 
where $\text{\tt TID}= \{1,\ldots,n\}$ is the set of thread ids}. 
\deleted{The} \added{Each} thread \deleted {of the program}
\added{$P_i$ is a loop-free program, which}
performs a sequence of memory access operations on a set of shared
memory objects and \cc memory fences.  The memory access operations
can be atomic or non-atomic in nature.
%
An instance of a thread operation in an execution is called an {\em
event}.  Events of a thread $t$ are uniquely indexed with an id.
%
\begin{definition}[Event]\newline
An event $i$ of thread $t$ is represented by a tuple $\langle i, t, act, obj,$ $ ord, inst \rangle$ where:
\begin{itemize}[label=inst,align=left,leftmargin=*]
\item [$act$] represents the event action $\in \{ \text{\tt read}, \text{\tt write}, \text{\tt rmw}, \text{\tt fence} \} $,
\item [$obj$] is the set of memory objects accessed,
\item [$ord$] records the \cc memory order associated with the event, and
\item [$inst$] is the corresponding program instruction.
\end{itemize}
\end{definition}
The $act$ {\tt rmw} represents {\em read-modify-write}.
%
Note that the set of memory objects of an rmw event can be non-singleton 
and for a fence event it is an empty set.
%
Let $\events$ denote the set of all program events. Furthermore,
$\writes$, $\reads$ and $\fences$ denote the write, read and fence 
events of the input program.
%
Throughout the text, use of read event as well as write event includes rmw
events unless specified otherwise.
%
\begin{definition}[Trace]\newline
\svs{The definition is cyclic, it uses $\events_\tau$ to define $\tau$. Also, I am not convinced why 
rf and mo together are insufficient and why we need hb additionally? }
\snj{$\events_\tau$ is just a representative symbol, it is not parametric on $\tau$.
The set $\events_\tau \subseteq \events$.}
	A trace or a maximal execution (or simply execution) $\tau$ of the input 
	program $P$ under \cc is a tuple 
	$\langle \events_\tau, \setHB, \setMO, \setRF \rangle$, where
	\begin{itemize}[label=sethb,align=left,leftmargin=*]
		\item [$\events_\tau$] represents the set of events in the trace $\tau$,
		\item [$\setHB$] ({\em Happen-before} relation) is a partial order on
			$\events_\tau$ representing the event interactions and inter-thread
			synchronizations, discussed in Section~\ref{sec:c11},
		\item [$\setMO$] ({\em Modification-order}) is a total order on the
			writes of an object that establishes coherence of $\tau$ 
			\wrt $\setHB$ , and
		\item [$\setRF$] ({\em Reads-from}) is a relation from a write event to
			a read event signifying that the read event takes the value of 
			the write event in $\tau$.
	\end{itemize}
\end{definition}

\noindent
{\bf Memory ordering under \cc}: 
The memory access and fence operations are
associated with ordering modes
that defines the ordering restriction \added{ on them.}
\snj{Technically, the restriction is on the events around the
current event, as stated in the following deleted line:}
\deleted{ placed on atomic and non-atomic access around atomic memory access.}
%
$\moset$ = $\{ \na, \rlx, \rel, \acq, \acqrel, \sc \}$, 
represents the orders relaxed (\rlx), release (\rel), acquire (\acq),
acquire-release (\acqrel) and sequentially consistent (\sc) for
atomic events. A non-atomic event has \na memory order associated with 
it.
%
We use $\ordevents{m}_\tau$ (and accordingly $\ordwrites{m}_\tau$, 
$\ordreads{m}_\tau$ and $\ordfences{m}_\tau$) to represent the $m$
ordered events of an execution sequence $\tau$ (where, $m \in \moset$);
for example $\ordwrites{\rel}_\tau$ represents the write events of 
$\tau$ with ordering restriction \rel. 
\svs{Why not use $o \in \moset$ representing order as a replacement?}
\snj{It makes the definitions very long and difficult to follow, 
eg: let $x \in \events_\tau$
$\^$ $ord(x) = \rel$ vs let $x \in \ordevents{\rel}_\tau$}

%\deleted{
%\noindent
%{\bf \cc fences}: \cc provides atomic thread fences or simply 
%fences to provide additional reordering restrictions on program 
%events. Note that \cc fences are not memory barriers and do not
%provide support for flushing local write values to shared memory.
%%
%A fence can be associated with memory orders $\acqrel$ and $\sc$
%providing varying degrees of reordering restrictions.}

\noindent
{\bf Buggy and fixed executions}: A program $P$ may contain {\em assert} 
instructions as correctness specification. 
\added{$P$ is considered buggy} when a trace of $P$ 
\deleted {that violates an 
assert check (\ie the condition in the assert check computes} \added{has an
assert expression evaluating} to
{\em false}. \deleted{is called a buggy trace.}
\snj{We are more interested in defining a buggy `traces'. 
So we can add in the end that such traces are called `buggy traces'.}


\textcolor{Maroon}{The purpose of this work 
is to synthesize \cc fences at appropriate
program locations to invalidate buggy traces. Particularly, the
event relation in the buggy traces with synthesized fences
render the resulting program behavior invalid under \cc, thus ensuring
that a previously buggy trace would not materialize as a 
\cc program execution.} \comment{Consider moving the above para to the Intro!}
\snj{We can state it in intro as well as here and thus keep reiterating our goal
to make it clear to the reader (provided we have the space.)}

\deleted{We represent the fixed trace corresponding to a
buggy trace $\tau$ by $\inv{\tau}$. 
%
As an intermediate step between $\tau$ and $\inv{\tau}$, we form an 
intermediate version of the trace $\tau$ with candidate fences
some of which are retained as a part of $\inv{\tau}$. We represent
the intermediate version of $\tau$ as $\imm{\tau}$. The details
of the intermediate step are discussed in Section~\ref{sec:methodology}.
%
We also use $\imm{P}$ and $\fx{P}$ to represent the intermediate and
fixed versions of the input program $P$.} \svs{I don't like the above para.}
\snj{The paragraph has been rewritten below:}


In the processes of invalidating a buggy trace $\tau$ of a program $P$,
$\tau$ undergoes two versions of transformations, an intermediate version
(represented as $\imm{\tau}$) and a final `invalidated' version (represented
as $\inv{\tau}$). The transformations have been discussed in 
Sections~\ref{sec:methodology} and \ref{sec:implementation}.
%
Note that once all the buggy traces $\tau$ have been transformed to 
the invalidated version
$\inv{\tau}$ by adding appropriate fences, we then consider the input 
program $P$ {\em fixed} or free of bugs (represented as $\fx{P}$). 